External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-13 CVPR2017_Review_Unified.tex
add
a

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{upgreek}
\usepackage{multirow}
\usepackage{color}
\usepackage{bm}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{arydshln}

\usepackage{cite}

@@

\section{External Prior Guided Internal Prior Learning}

@@

We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ The best PSNR result is highlighted in bold.\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB. Due to the space limitations, the visual comparisons are provided in the supplementary file.

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{upgreek}
\usepackage{multirow}
\usepackage{color}
\usepackage{bm}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{arydshln}
\usepackage{cite}

%\usepackage{sectsty}
%\sectionfont{\fontsize{12}{11}\selectfont\leftskip=0pt\vspace{-2mm}}
%\subsectionfont{\fontsize{11}{10}\selectfont\leftskip=0pt\vspace{-1mm}}
%\subsubsectionfont{\fontsize{10}{10}\selectfont\leftskip=0pt\vspace{-1mm}}

@@

\section{External Prior Guided Internal Prior Learning and Denoising}

@@

We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ The best result is highlighted in bold.\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB. Due to the space limitations, the visual comparisons are provided in the supplementary file.
